### 2015-03-16 Docs/managing_jobs/managingjobs.tex
more about why we prefer rhea over titan for yt-ing

The best way to do visualization is to use rhea, the OLCF vis machine.
You need to build \yt\ via the {\tt install\_script.sh} script {\em on
rhea}.  It also must be on a Lustre filesystem, so it is seen by
the compute node.  It is best to build it in your {\tt \$PROJWORK} directory,
since that has a longer time between purges.  Once the installation is
complete, it will tell you what script to source to define the
necessary paths.

@@

@@

You can run \yt\ python scripts in the titan batch queues to do your
visualization.  You need to install \yt\ and all its dependencies
manually somewhere on a LUSTRE filesystem---this ensures that the
compute nodes can see it.  A good choice is the project space, since
that has a longer purge window.

@@

The scripts {\tt vis-titan.run} and {\tt parallel-yt-new} in {\tt
MAESTRO/Util/job\_scripts/titan/} will manage the yt jobs by calling a
python script for each file that matches a pattern.  Make sure you set
the proper path for the \yt\ {\tt activate} script in {\tt
parallel-yt-new}---this ensures that the paths to the various libraries
are set on the compute nodes.

Note that the actual visualization command itself is launched by
{\tt parallel-yt-new} using the {\tt aprun} command.

>>>>

The best way to do visualization is to use rhea, the OLCF vis machine.
You need to build \yt\ via the {\tt install\_script.sh} script {\em on
rhea}.  It also must be on a {\em Lustre filesystem}, so it is seen by
the compute node.  It is best to build it in your {\tt \$PROJWORK} directory,
since that has a longer time between purges.  Once the installation is
complete, it will tell you what script to source to define the
necessary paths.

@@

Note: the line in {\tt parallel-yt-rhea} that {\tt source}s the \yt\
{\tt activate} script may need to be modified to point to the
correct \yt\ installation path.

@@

You can also run \yt\ python scripts in the titan batch queues to do your
visualization.  You need to install \yt\ and all its dependencies
manually somewhere on a {\em Lustre filesystem}---this ensures that the
compute nodes can see it.  A good choice is the project space, since
that has a longer purge window.

@@

The scripts {\tt vis-titan.run} and {\tt parallel-yt-new} in {\tt
MAESTRO/Util/job\_scripts/titan/} will manage the \yt jobs by calling a
python script for each file that matches a pattern.  Make sure you set
the proper path for the \yt\ {\tt activate} script in {\tt
parallel-yt-new}---this ensures that the paths to the various libraries
are set on the compute nodes.

Note that the actual visualization command itself is launched by
{\tt parallel-yt-new} using the {\tt aprun} command.  This is the
only way to get a job to run on the compute nodes on titan.  But
{\tt aprun} can only launch a single job at a time, so this means
we cannot easily do (trivally) parallel visualization on a node.  For
this reason, running on rhea is preferred.
